---
title: "Notes as a landing page?"
author: "Anthony Davidson"
date: "02/02/2020"
vignette: >
  %\VignetteIndexEntry{aRxiv tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8](inputenc)
---

[arXiv](https://arxiv.org) is a repository of electronic preprints for
computer science, mathematics, physics, quantitative biology,
quantitative finance, and statistics. The
[aRxiv package](https://github.com/ropensci/aRxiv) provides an
[R](https://www.r-project.org) interface to the
[arXiv API](https://arxiv.org/help/api/index).

Note that the arXiv API _does not_ require an API key.

```{r be_graceful_on_cran, include=FALSE}
# if on cran, avoid errors when connection problems
on_cran <- Sys.getenv("NOT_CRAN")!="true"
if(on_cran) {
    aRxiv:::set_arxiv_timeout(1)
    aRxiv:::set_message_on_timeout(TRUE)
}
```

```{r change_aRxiv_delay_option, include=FALSE}
options(aRxiv_delay=0.5)
```

## Installation

You can install the [aRxiv package](https://github.com/rOpenSci/aRxiv)
via [CRAN](https://cran.r-project.org):

```{r install_from_cran, eval=FALSE}
install.packages("aRxiv")
```

Or use `devtools::install_github()` to get the (possibly more recent) version
at [GitHub](https://github.com/rOpenSci/aRxiv):

```{r install_pkgs, eval=FALSE}
install.packages("devtools")
library(devtools)
install_github("ropensci/aRxiv")
```

## Basic use

Use `arxiv_search()` to search [arXiv](https://arxiv.org),
`arxiv_count()` to get a simple count of manuscripts matching a
query, and `arxiv_open()` to open the abstract pages for a set of
results from `arxiv_search()`.

We'll get to the details in a moment. For now, let's look at a few
examples.

Suppose we wanted to identify all arXiv manuscripts with &ldquo;`Peter
Hall`&rdquo; as an author. It is best to first get a count, so that we have
a sense of how many records the search will return. (Peter Hall was
&ldquo;[among the world's most prolific and highly cited authors in both probability and statistics](https://en.wikipedia.org/wiki/Peter_Gavin_Hall).&rdquo;)
We first use `library()` to load the aRxiv package and then
`arxiv_count()` to get the count.

```{r arxiv_count}
library(aRxiv)
# arxiv_count('au:""')
# 
# #search options?
# arxiv_search("submittedDate:[20201701010000 TO 20201701012400]", limit=2)
# rec <- arxiv_search('au:"Peter Hall"', limit=100)
# nrow(rec)

```

